High-Throughput-derived Biologically-Inspired Features for Unconstrained Face Recognition

### 2011-11-28 methods.tex
Missing references, typos
More fixes
Edits in response to reviewers
FIX: minor edits

\begin{figure*}[ht]
\begin{center}
	\rule{1\linewidth}{0pt}
        \includegraphics[width=0.75\linewidth]{figures/models_v2.pdf}
\end{center}
   \caption{{\bf A schematic diagram of the system architecture of the family of
       models considered.}  Each model consists of one to three feedforward
     filtering layers, with the filters in each layer being applied across the
     previous layer.}
\label{fig:models}
\end{figure*}

@@

A total of 5,915 \emph{HT-L2} and 6,917 \emph{HT-L3} models were screened on the \emph{LFW}
View 1 ``aligned'' set \cite{taigman:bmvc09}.  We selected the best five models
from each ``pool'' for further analysis on the \emph{LFW} View 2 set (Restricted
Protocol).  Note that \emph{LFW} View 1 and View 2 do not contain the same
individuals and are thus mutually exclusive sets. View 1 was designed as a model
selection set while View 2 is used as an independent validation set for the
purpose of comparing different methods.

@@

\subsection{Additional Testing with Synthetic Face Images}

In order to assess model performance on an image set with a known amount of variation, 
we generated a set of 3D-rendered face images.  3D face meshes were randomly generated
using the FaceGen \cite{facegen} software package and were rendered using
the free POV-Ray ray-tracer \cite{povray}.  For each rendered image, a model rotation 
(azimuth and elevation), position (x and y), and scale were drawn from a uniform 
distribution and the models were rendered with a common light source (Figure \ref{fig:variation_levels}).  
For the experiments presented here, rotation, size, and position were combined into
a single composite ``variation level'' wherein the variation in the pixel-level euclidean norm
was equalized for each kind of variation (e.g. one ``unit'' of rotation variation produced an
equivalent pixel-level change as one ``unit'' of position variation).  Examples of several
variation ``levels'' are shown in Figure \ref{fig:variation_levels}.

>>>>

\begin{figure*}[ht]
\begin{center}
	\rule{1\linewidth}{0pt}
        \includegraphics[width=1\linewidth]{figures/models_v2.pdf}
\end{center}
   \caption{{\bf A schematic diagram of the system architecture of the family of
       models considered.}  Each model consists of one to three feedforward
     filtering layers, with the filters in each layer being applied across the
     previous layer.}
\label{fig:models}
\end{figure*}

@@

A total of 5,915 \emph{HT-L2} and 6,917 \emph{HT-L3} models were screened on the \emph{LFW}
View 1 ``aligned'' set \cite{taigman:bmvc09}.  We selected the best five models
from each group for further analysis on the \emph{LFW} View 2 set (Restricted
Protocol).  Note that \emph{LFW} View 1 and View 2 do not contain the same
individuals and are thus mutually exclusive sets. View 1 was designed as a model
selection set while View 2 is used as an independent validation set for the
purpose of comparing different methods.

@@

\subsection{Additional Testing with Synthetic Face Images}
\label{synthetic_methods}

In order to assess model performance on an image set with a known amount of variation, 
we generated a set of 3D-rendered face images.  3D face meshes were randomly generated
using the FaceGen software package and were rendered using
the free POV-Ray ray-tracer.  For each rendered image, a model rotation 
(azimuth and elevation), position (x and y), and scale were drawn from a uniform 
distribution and the models were rendered with a common light source (Figure \ref{fig:variation_levels}).  
For the experiments presented here, rotation, size, and position were combined into
a single composite ``variation level'' wherein the variation in the pixel-level euclidean norm
was equalized for each kind of variation (e.g. one ``unit'' of rotation variation produced an
equivalent pixel-level change as one ``unit'' of position variation).  Examples of several
variation ``levels'' are shown in Figure \ref{fig:variation_levels}.

### 2011-11-28 results.tex
FIX: minor edits

The synthetic face evaluation sets used here provide us with the ability to parametrically control the level of rotation, position and scale variation that our models are required to tolerate.  Figure \ref{fig:perf_variation_levels} shows the performance the best models from each model class (V1-like, HT-L2, HT-L3) as a function of (composite) variation level for an eight-way face classification task.

>>>>

The synthetic face evaluation sets used here provide us with the ability
to parametrically control the level of rotation, position and scale
variation that our models are required to tolerate.  Figure
\ref{fig:perf_variation_levels} shows the performance of the best models
from each model class (V1-like, HT-L2, HT-L3) as a function of
(composite) variation level for an eight-way face classification task.
